---
title: "git_backed_test"
format: html
---

## Steps

1. First create a directory / RStudio project for the document
1. Create a boilerplate version of your `report.qmd` file 
1. Run `rsconnect::writeManifest()` within this project. Make sure the manifest doesn't capture any sensitive / large data!
1. Commit your report and the manifest to the git repo
1. Push the changes to GitHub
1. From the Connect server main page in a browser, go `Content > Publish > Import from Git`
1. Enter the repo URL

Additional details for more complicated configurations [here](https://docs.posit.co/connect/user/git-backed/).

## Tests

Let's try reading a file from `/n/data1/hms/ccb/resources/`. This is a data
frame with two columns and 10^8^ rows. I created it like this (this chunk is not evaluated by this document):

```{r}
#| eval: false

library(data.table)

x = data.table(i = 1:1e8, x = rnorm(1e8))

```

It's pretty big so we can test the network speed between
`/n/data1/hms/ccb/resources/` and the Connect server:

```
> object.size(x) |> format(units = "auto")
[1] "1.1 Gb"
```

It's 2.6GB on disk as a tsv. Let's try to read it in and time how long it takes:

```{r}
library(data.table)

setDTthreads(1) # not sure what the Connect server would default to

system.time({x <- fread("/n/data1/hms/ccb/resources/git_backed_test/data/x.tsv")})

x
```

For comparison that `fread()` takes 6.7 seconds on an O2 compute node using 1 thread.

